On the power of oritatami cotranscriptional folding with unary bead sequence\thanks{This work is supported in part by KAKENHI Grant-in-Aid for Challenging Research (Exploratory) No.~18K19779 and JST Program to Disseminate Tenure Tracking System No.~6F36 granted to S.~Z.~F. and S.~S.}

### 2018-11-24 paper.tex
Section 3 done
Problem 1 was added to Section 3.

In \cite{DemaineDNA24}, Demaine et al. proved that at delay 1 and arity 1, an oritatami system can fold upon the seed of size $n$ only the first $9n$ beads of a transcript deterministically. 
We consider this finiteness problem under various settings of the values of delay and arity. 
Results on this problem are summarized in Fig.~\ref{fig:summary}.

>>>>

In \cite{DemaineDNA24}, Demaine et al. proved that at delay 1 and arity 1, an oritatami system can fold upon the seed of size $n$ only the first $9n$ beads of a transcript deterministically. 
We consider this finiteness problem for unary oritatami systems under various settings of the values of delay and arity, which is formalized as follows.

\begin{problem}\label{prob:det_unary_length}
Give an upper bound on the length of a transcript of a delay-$\delta$, arity-$\alpha$ deterministic unary oritatami system whose seed is of length $n$ by a function in $\delta$, $\alpha$, and $n$. 
\end{problem}

Results on this problem are summarized in Fig.~\ref{fig:summary}.
